---
title: Reproducibility - Preserving Survey Data
author:
  - Laurel Krovetz
  - Lars Vilhuber
date: June 2025
---

```{r config,include=FALSE}
library(readr)
library(here)
library(knitr)
library(dplyr)
library(ggplot2)
library(qualtRics)
library(lubridate)
library(qrcode)

# Qualtrics secrets are read from the environment:
# - QUALTRICS_API_KEY
# - QUALTRICS_BASE_URL

# We also need DATAVERSE secrets
#      DATAVERSE_TOKEN: ${{secrets.DATAVERSE_TOKEN}}
#      DATAVERSE_SERVER: https://demo.dataverse.org
#      DATAVERSE_DATASET_DOI: do
# Let's check that they are there:

message(Sys.getenv("QUALTRICS_BASE_URL"))

# The repository name

message(Sys.getenv("GITHUB_REPOSITORY"))

# Process the repository name to generate the URL
# - split the two components
# - combine them into a URL with 'github.io' in the middle

GITHUB_REPOSITORY <- Sys.getenv("GITHUB_REPOSITORY")
GITHUB_REPOSITORY_PARTS <- strsplit(GITHUB_REPOSITORY, "/")[[1]]
REPOSITORY_URL <- paste0("https://github.com/", GITHUB_REPOSITORY)
WEBSITE_URL <- paste0("https://", GITHUB_REPOSITORY_PARTS[1], ".github.io/", GITHUB_REPOSITORY_PARTS[2])

# qualtRics data:
# you can find this with all_surveys() %>% arrange(creationDate) %>% head()

QUALTRICS_FULL_URL <- "https://cornell.yul1.qualtrics.com/jfe/form"

# Public Qualtrics URL for day 2

QUALTRICS_SURVEY <- "SV_cNkhKL69K2Ob7o2"

# Time when this was posted (discard anything before that)

QUALTRICS_STIME <- ymd_hms("2025-04-30 23:59:00")
QUALTRICS_ETIME <- ymd_hms("2025-05-26 23:59:00")


if (!dir.exists(here::here("data"))) {
  dir.create(here::here("data"))
}
```

::: {.panel-tabset}

## Introduction

Here we will demonstrate how to preserve raw survey data and also how to handle confidential data. We will do so with data from a  survey that you all will provide responses to. Some of the questions are meant to elicit "confidential" information from you as responses. You should not give your actual confidential information in response to these questions. We will use these questions as way to teach how to preserve data when some data are confidential. 


## Live Survey 

Please fill out this  survey:

<`r file.path(QUALTRICS_FULL_URL,QUALTRICS_SURVEY)`>

### Live Results
```{r downloaddata,include=FALSE}
# download data to local location

# if the Qualtrics API key is not set, we can't fetch the data
if (Sys.getenv("QUALTRICS_API_KEY") != "") {
  data.raw <- fetch_survey(surveyID = QUALTRICS_SURVEY, verbose = TRUE) 
  data <- data.raw |>
          filter(Status != "Survey Preview") |>
          filter(Consent == "I agree that my data will be used in the manner described.") |>
          filter(StartDate > QUALTRICS_STIME & EndDate < QUALTRICS_ETIME) |>
    # renaming variables
    select(StartDate,EndDate,Status,Finished,RecordedDate,ResponseId,Consent,Preferred_topic,Degree,JEL_primary,
          starts_with("JEL_secondary"),starts_with("Versioning_"))
} else {
  data <- data.frame()
}

```

```{r create_table2, results='asis', include=TRUE,echo=FALSE,message=FALSE}

if ( nrow(data) >0 ) {
data |>
  select(Preferred_topic) |>
  group_by(Preferred_topic) |>
  summarise(Frequency=n()) |>
  ungroup() |>
  mutate(Percent = round(Frequency/nrow(data)*100,2)) -> data.table

data.table |> kable()
} else {
  cat("No data yet. Check back later.")
}
```

## Why

Lorem ipso facto.

:::